Interval Probability for Fuzzy Quantum Theories

### 2016-06-30 prob.tex
prob.tex Fix a bug by replacing "\mu'^B" by "\mu^{\prime B}"

Naturally, we may ask: is every probability measure induced from a
state by the Born rule? The answer is yes by Gleason's theorem when
the dimension~$\ge3$~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
Furthermore, a simple corollary of Gleason's theorem can show the
Born rule is the unique function satisfying conditions 1. to 3.
\begin{cor}
The Born rule is the unique function satisfying conditions 1. to 3.
\end{cor}
\begin{proof}
Assume there is another function $\mu'^B$ such that $\mu'^B_{\rho}$
is a quantum probability measure for all mixed state~$\rho$. We
are going to prove $\mu'^B=\mu^B$.

Fix a pure normalized state $\phi$, $\mu'^B_{\phi}$ is a quantum
probability measure by condition 2. By Gleason's theorem, there is
a mixed state ~$\rho'$, such that $\mu'^B_{\phi}\left(P\right)=\Tr\left(\rho'P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P\right)$
for all event $P$.

Consider the event $P'=\mathbb{1}-\proj{\phi}$, we have 
\begin{eqnarray*}
0 & \overset{\textrm{Condition 3}}{=} & \mu^B_{\phi}\left(P'\right)\\
 & = & \sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P'\right)
\end{eqnarray*}
Because $q_{j}>0$, we have $\mu^B_{\psi_{j}}\left(P\right)=0$,
i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $P'$.
However, the only subspace orthogonal to $P'$ is span by $\ket{\phi}$.
Hence, $\mu'^B_{\phi}=\mu^B_{\phi}$.
\end{proof}

>>>>

Naturally, we may ask: is every probability measure induced from a
state by the Born rule? The answer is yes by Gleason's theorem when
the dimension~$\ge3$~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
Furthermore, a simple corollary of Gleason's theorem can show the
Born rule is the unique function satisfying conditions 1. to 3.
\begin{cor}
The Born rule is the unique function satisfying conditions 1. to 3.
\end{cor}
\begin{proof}
Assume there is another function $\mu^{\prime B}$ such that $\mu^{\prime B}_{\rho}$
is a quantum probability measure for all mixed state~$\rho$. We
are going to prove $\mu^{\prime B}=\mu^B$.

Fix a pure normalized state $\phi$, $\mu^{\prime B}_{\phi}$ is a quantum
probability measure by condition 2. By Gleason's theorem, there is
a mixed state ~$\rho'$, such that $\mu^{\prime B}_{\phi}\left(P\right)=\Tr\left(\rho'P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P\right)$
for all event $P$.

Consider the event $P'=\mathbb{1}-\proj{\phi}$, we have 
\begin{eqnarray*}
0 & \overset{\textrm{Condition 3}}{=} & \mu^B_{\phi}\left(P'\right)\\
 & = & \sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P'\right)
\end{eqnarray*}
Because $q_{j}>0$, we have $\mu^B_{\psi_{j}}\left(P\right)=0$,
i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $P'$.
However, the only subspace orthogonal to $P'$ is span by $\ket{\phi}$.
Hence, $\mu^{\prime B}_{\phi}=\mu^B_{\phi}$.
\end{proof}
